Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2022-10-28 analysis/paper_draft3.Rmd
updated batson workflow fig; added appendix heading

```{r batsonworkflowfig, fig.cap="Batson workflow"}

library(DiagrammeR)
grViz(diagram = "digraph flowchart {
  rankdir = LR
  node [fontname = arial, shape = rectangle]
  tab1 [label = '@@1']
  tab2 [label = '@@2']
  tab3 [label = '@@3']

  tab1 -> tab2 -> tab3;
}

  [1]: 'prima facie case'
  [2]: 'proffered reasons'    
  [3]: 'prove bias'    
  ", height = '100%', width = '100%')

@@

>>>>

```{r batsonworkflowfig, fig.cap="Batson workflow", fig.align = 'center', out.width="50%", fig.pos = "h"}

load_path <- here::here("figures","batson_workflow_fig.png")
knitr::include_graphics(load_path)

@@

<div id="refs"></div>

# Appendix

Insert appendix here.
